\documentclass[10pt]{extarticle}
\input{preamble}

\begin{document}
\makecvheader

\cvheading{Education}
  
\organdloc{\href{https://www.washington.edu/}{University of Washington}}{Seattle, WA}
\jobanddate{\href{https://cs.washington.edu/}{Ph.D. in Computer Science \& Engineering}}{Jun 2023 -- May 2028 (Expected)}

\begin{itemize}
    \item Advisor: Prof. \href{http://bariskasikci.org/}{Baris Kasikci}.
\end{itemize}

\organdloc{\href{https://www.u-tokyo.ac.jp/en/}{The University of Tokyo}}{Tokyo, Japan}
\jobanddate{\href{https://www.is.s.u-tokyo.ac.jp/en/}{B.Sc. in Information Science}}{Apr 2019 -- Mar 2023}
\begin{itemize}
    \item Advisor: Prof. \href{https://sites.google.com/site/shinyaty/home}{Shinya Takamaeda-Yamazaki}.
\end{itemize}

\cvheading{Publications}
\noindent Google Scholar: \url{https://scholar.google.com/citations?user=IMZC2hYAAAAJ}\\
\noindent Semantic Scholar: \url{https://www.semanticscholar.org/author/Keisuke-Kamahori/2283847574}\\
\noindent (* denotes equal contribution)\\
\needspace{3\baselineskip}\noindent {\large \textbf{Preprints}}
\begin{enumerate}[label={[P\arabic*]}]
% VibeServe
\item 
\publicationentry{
    \href{https://arxiv.org/abs/2605.06068}{VibeServe: Can AI Agents Build Bespoke LLM Serving Systems?}
}{
    Keisuke Kamahori*, Shihang Li*, Simon Peter, Baris Kasikci.
}{
    Preprint, under submission. (Presented at \href{https://dl4c.github.io/}{DL4C Workshop} @ \href{https://icml.cc/Conferences/2026}{ICML 2026}, July 2026.)
}
\label{pub:vibeserve}

% M*
\item 
\publicationentry{
    \href{https://arxiv.org/abs/2606.12688}{M*: A Modular, Extensible, Serving System for Multimodal Models}.
}{
    Atindra Jha*, Naomi Sagan*, Keisuke Kamahori$\dagger$, Irmak Sivgin$\dagger$, Rohan Sanda, Steven Gao, Mark Horowitz, Luke Zettlemoyer, Olivia Hsu, Jure Leskovec, Baris Kasikci, Stephanie Wang.
}{
    Preprint, under submission.
}
\label{pub:mstar}

% Murmur
\item 
\publicationentry{
    \href{https://arxiv.org/abs/2606.01483v1}{Murmur: An Efficient Inference System for Long-Form ASR}.
}{
    Wei-Tzu Lee, Keisuke Kamahori, Baris Kasikci.
}{
    Preprint, under submission. (Presented at \href{https://mlsys.org/Conferences/2026/CallForYPS}{MLSys 2026 YPS}, May 2026.)
}
\label{pub:murmur}

% VoxServe
\item 
\publicationentry{
    \href{https://arxiv.org/abs/2602.00269}{VoxServe: Streaming-Centric Serving System for Speech Language Models}.
}{
    Keisuke Kamahori, Wei-Tzu Lee, Atindra Jha, Rohan Kadekodi, Stephanie Wang, Arvind Krishnamurthy, Baris Kasikci.
}{
    Preprint, under submission. 
}
\label{pub:voxserve}

% AgentFlux
\item 
\publicationentry{
    \href{https://arxiv.org/abs/2510.00229}{AgentFlux: Decoupled Fine-Tuning \& Inference for On-Device Agentic Systems}.
}{
    Rohan Kadekodi*, Zhan Jin*, Keisuke Kamahori, Yile Gu, Sean Khatiri, Noah H. Bayindirli, Sergey Gorbunov, Baris Kasikci.
}{
    Preprint, under submission.
}
\label{pub:agentflux}

% anonymized preprint
\item
\publicationentry{
    [Title omitted to maintain anonymity] (Topic: profile-guided optimization for CPU prefetchers).
}{
    Keisuke Kamahori et al.
}{
    Under submission.
}
\label{pub:prefetcher}

\end{enumerate}
\needspace{3\baselineskip}\noindent {\large \textbf{Peer-Reviewed Conferences}}

\begin{enumerate}[label={[C\arabic*]}]
% ConsumerBench
\item 
\publicationentry{
    \href{https://arxiv.org/abs/2506.17538}{ConsumerBench: Benchmarking Generative AI Applications on End-User Devices}.
}{
    Yile Gu*, Rohan Kadekodi*, Hoang Nguyen, Keisuke Kamahori, Yiyu Liu, Baris Kasikci.
}{
    \href{https://colmweb.org/}{COLM 2026}, October 2026.
}
\label{pub:consumerbench}

% TeleRAG 
\item 
\publicationentry{
    \href{https://arxiv.org/abs/2502.20969}{TeleRAG: Efficient Retrieval-Augmented Generation Inference with Lookahead Retrieval}.
}{
    Chien-Yu Lin*, Keisuke Kamahori*, Yiyu Liu*, Xiaoxiang Shi, Madhav Kashyap, Yile Gu, Rulin Shao, Zihao Ye, Kan Zhu, Stephanie Wang, Arvind Krishnamurthy, Rohan Kadekodi, Luis Ceze, Baris Kasikci.
}{
    \href{https://mlsys.org/Conferences/2026}{MLSys 2026}, May 2026.
}
\label{pub:telerag}

% LiteASR
\item 
\publicationentry{
    \href{https://arxiv.org/abs/2502.20583}{LiteASR: Efficient Automatic Speech Recognition with Low-Rank Approximation}.
}{
    Keisuke Kamahori, Jungo Kasai, Noriyuki Kojima, Baris Kasikci.
}{
    \href{https://2025.emnlp.org/}{EMNLP 2025} (Main), November 2025. (Featured on Hugging Face's \href{https://huggingface.co/spaces/hf-audio/open_asr_leaderboard}{Open ASR Leaderboard}.)
}
\label{pub:liteasr}

% NanoFlow
\item 
\publicationentry{
    \href{https://arxiv.org/abs/2408.12757}{NanoFlow: Towards Optimal Large Language Model Serving Throughput}.
}{
    Kan Zhu, Yufei Gao, Yilong Zhao, Liangyu Zhao, Gefei Zuo, Yile Gu, Dedong Xie, Tian Tang, Qinyu Xu, Zihao Ye, Keisuke Kamahori, Chien-Yu Lin, Ziren Wang, Stephanie Wang, Arvind Krishnamurthy, Baris Kasikci.
}{
    \href{https://www.usenix.org/conference/osdi25}{OSDI 2025}, July 2025.
}
\label{pub:nanoflow}

% Fiddler
\item 
\publicationentry{
    \href{https://arxiv.org/abs/2402.07033}{Fiddler: CPU-GPU Orchestration for Fast Inference of Mixture-of-Experts Models}.
}{
    Keisuke Kamahori*, Tian Tang*, Yile Gu, Kan Zhu, Baris Kasikci.
}{
    \href{https://iclr.cc/Conferences/2025}{ICLR 2025}, April 2025. (Also presented at \href{https://pml4dc.github.io/iclr2024/}{PML4LRS} @ \href{https://iclr.cc/Conferences/2024}{ICLR 2024}, May 2024.)
}
\label{pub:fiddler}

% ASPLOS 2024
\item 
\publicationentry{
    \href{https://doi.org/10.1145/3623278.3624750}{Manticore: Hardware-Accelerated RTL Simulation with Static Bulk-Synchronous Parallelism}.
}{
    Mahyar Emami*, Sahand Kashani*, Keisuke Kamahori, Mohammad Sepehr Pourghannad, Ritik Raj, James R. Larus.
}{
    \href{https://www.asplos-conference.org/asplos2024/}{ASPLOS 2024}, April 2024.
}
\label{pub:manticore}

% FPGA 2024
\item 
\publicationentry{
    \href{https://dl.acm.org/doi/10.1145/3626202.3637579}{A 475 MHz FPGA Accelerator for RTL Simulation}.
}{
    Sahand Kashani*, Mahyar Emami*, Keisuke Kamahori, Mohammad Sepehr Pourghannad, Ritik Raj, James R. Larus.
}{
    \href{https://www.isfpga.org/}{FPGA 2024}, March 2024.
}
\label{pub:manticore-fpga}

% SIGCOMM
\item 
\publicationentry{
    \href{https://doi.org/10.1145/3546037.3546059}{CiraaS: cloud computing with programmable logic}.
}{
    Kenji Tanaka, Yuki Arikawa, Tsuyoshi Ito, Yuki Matsuda, Keisuke Kamahori, Shinya Kaji, Takeshi Sakamoto.
}{
    \href{https://conferences.sigcomm.org/sigcomm/2022/}{SIGCOMM 2022} Poster and Demo Sessions, August 2022.
}
\label{pub:2022sigcomm}

% HEART
\item 
\publicationentry{
    \href{https://doi.org/10.1145/3535044.3535048}{Accelerating Decision Tree Ensemble with Guided Branch Approximation}.
}{
    Keisuke Kamahori, Shinya Takamaeda-Yamazaki.
}{
    \href{https://heart2022.lila.cs.tsukuba.ac.jp/heart2022}{HEART 2022}, June 2022.
}
\label{pub:2022heart}

% YArch
\item 
\publicationentry{
    \href{https://www.youtube.com/watch?v=hE5U6xIqBNk}{GBA: Guided Branch Approximation}.
}{
    Keisuke Kamahori, Shinya Takamaeda-Yamazaki.
}{
    \href{https://web.mit.edu/yarch2022/index.html}{YArch 2022} (Co-located with \href{https://asplos-conference.org/2022/}{ASPLOS 2022}), March 2022.
}
\label{pub:2022yarch}

\end{enumerate}

\cvheading{Experience}

% UW
\organdloc{\href{https://www.washington.edu/}{University of Washington}}{Seattle, WA}
\jobanddate{Ph.D. Student, \href{https://syfi.cs.washington.edu/}{Systems for Future Intelligence (SyFI) Lab}}{Jun 2023 -- Present}
\begin{itemize}
    \item Supervisor: Prof. \href{http://bariskasikci.org/}{Baris Kasikci}.
    \item \textbf{Agents and Systems}: Developing an AI agent system for serving system development (VibeServe \ref{pub:vibeserve}); an efficient fine-tuning framework for local AI agents (AgentFlux \ref{pub:agentflux}); part of the \href{https://sds.cs.washington.edu/people/}{Self-Defining Systems} project.
    \item \textbf{Systems for Multimodal Models}: Developing a universal serving system for multimodal models (M* \ref{pub:mstar}); a streaming-centric serving system for speech LLMs (VoxServe \ref{pub:voxserve}); a compression technique for speech models (LiteASR \ref{pub:liteasr}); collaborating with \href{https://ai4deafblind.org/}{AI4DeafBlind} to enable fast ASR inference on low-resource accessibility devices.
    \item \textbf{Local AI}: Led projects on inference acceleration for RAG (TeleRAG \ref{pub:telerag}) and MoE models (Fiddler \ref{pub:fiddler}) under resource constraints; benchmarked on-device inference (ConsumerBench \ref{pub:consumerbench}).
    \item \textbf{Computer Architecture}: Designed profile-guided optimization techniques for data center CPU prefetchers (under submission \ref{pub:prefetcher}).
\end{itemize}

% NVIDIA
\organdloc{\href{https://www.nvidia.com/en-us/}{NVIDIA}}{Santa Clara, CA}
\jobanddate{Architect Intern}{Jun 2026 -- Sep 2026}
\begin{itemize}
    \item Supervisor: \href{https://www.linkedin.com/in/joydeep-ray-0563591/}{Joydeep Ray}.
    \item Working on architectural modeling and simulation for future GPU generations optimized for AI inference.
\end{itemize}

% Kotoba
\organdloc{\href{https://site.kotoba.tech/}{Kotoba Technologies Inc.}}{Seattle, WA / Tokyo, Japan}
\jobanddate{Founding Engineer}{Jun 2024 -- Jul 2025}
\begin{itemize}
    \item One of the earliest engineers at a startup building speech AI (backed by USD 23M in seed funding), with a focus on real-time speech-to-speech translation.
    \item Led the design and implementation of the serving infrastructure powering \href{https://apps.apple.com/app/id6740851285}{DOTSU}, the company's core simultaneous translation product (500K+ sessions in three months), and APIs (ASR, TTS, STS), involving full-stack optimization tailored to the unique duplex architecture and strict latency requirements of real-time speech LLMs.
\end{itemize}

% Fixstars
\organdloc{\href{https://www.fixstars.com/en/}{Fixstars Corporation}}{Tokyo, Japan}
\jobanddate{FPGA Engineer}{Aug 2021 -- May 2023}
\begin{itemize}
    \item Supervisor: Shinya Kaji.
    \item Developed an FPGA accelerator for distributed 3D Fast Fourier Transform workloads.
    \item Contributed to a research project on FPGA SmartNICs for data centers \ref{pub:2022sigcomm}.
\end{itemize}

% CASYS
\organdloc{\href{https://www.u-tokyo.ac.jp/en/}{The University of Tokyo}}{Tokyo, Japan}
\jobanddate{Undergraduate Researcher, \href{https://sites.google.com/view/casys/}{Laboratory for Computer Architecture and Systems}}{Aug 2021 -- Mar 2023}
\begin{itemize}
    \item Supervisor: Prof. \href{https://sites.google.com/site/shinyaty/home}{Shinya Takamaeda-Yamazaki}.
    \item Designed an acceleration method based on microarchitectural support for approximate computing \ref{pub:2022heart}, \ref{pub:2022yarch}.
\end{itemize}

% EPFL
\organdloc{\href{https://www.epfl.ch/en/}{École Polytechnique Fédérale de Lausanne}}{Lausanne, Switzerland}
\jobanddate{Research Intern, \href{https://www.epfl.ch/labs/vlsc/}{Very Large Scale Computing Lab.}}{Jul 2022 -- Sep 2022}
\begin{itemize}
    \item Supervisor: Prof. \href{https://people.epfl.ch/james.larus}{James Larus}.
    \item Designed an FPGA accelerator for hardware simulation \ref{pub:manticore}, \ref{pub:manticore-fpga}.
\end{itemize}

% NAIST
\organdloc{\href{http://www.naist.jp/en/}{Nara Institute of Science and Technology}}{Nara, Japan}
\jobanddate{Research Intern, \href{http://archlab.naist.jp/}{Computing Architecture Lab.}}{Feb 2022 -- Mar 2022}
\begin{itemize}
    \item Supervisors: Prof. \href{https://scholar.google.com/citations?user=Tp_fVdEAAAAJ&hl=en}{Yasuhiko Nakashima} and Prof. \href{https://scholar.google.com/citations?user=f8UqgYIAAAAJ&hl=en}{Renyuan Zhang}.
    \item Worked on lightweight neural network processing with stochastic computing.
\end{itemize}

% Matsuo Lab
\organdloc{\href{https://www.u-tokyo.ac.jp/en/}{The University of Tokyo}}{Tokyo, Japan}
\jobanddate{Research Intern, \href{https://weblab.t.u-tokyo.ac.jp/en/}{Matsuo Lab.}}{Dec 2020 -- Mar 2022}
\begin{itemize}
    \item Supervisors: Prof. \href{http://ymatsuo.com/index.html}{Yutaka Matsuo} and \href{https://www.linkedin.com/in/ryookada-5298765a/}{Ryo Okada}.
    \item Worked on extracting human-interpretable knowledge from high-dimensional deep RL models.
\end{itemize}

% Nagase
\organdloc{\href{https://www.toshin.com/nagase/}{Nagase Brothers Inc.}}{Tokyo, Japan}
\jobanddate{AI Engineer}{May 2020 -- Aug 2021}
\begin{itemize}
    \item Worked on developing software using deep learning techniques for educational services.
\end{itemize}

% GSoC
\organdloc{\href{https://root.cern.ch/}{ROOT}, \href{https://hepsoftwarefoundation.org/}{HEP Software Foundation}}{Remote}
\jobanddate{Google Summer of Code Student}{May 2020 -- Aug 2020}
\begin{itemize}
    \item Supervisor: Dr. \href{https://github.com/oshadura}{Oksana Shadura}.
    \item Contributed to an open-source data analysis framework for the high-energy physics community in a Google Summer of Code project titled ``\href{https://kamahori.github.io/gsoc2020/}{Pre-conditioners applied to ROOT compression algorithms}.''
\end{itemize}

% awards
\cvheading{Awards and Grants}

\begin{itemize}
    \item \href{https://mlsys26.flashinfer.ai/}{MLSys 2026 Competition - NVIDIA Track (FlashInfer AI Kernel Generation Contest)} \dateright{May 2026}\\
    {\it 1st place (GDN Track, Full-Agent), 2nd place (GDN Track, Agent-Assisted), and 3rd place (DSA Track, Full-Agent)}\\
    {\it Awarded NVIDIA DGX Spark, RTX 5090, and RTX 5080}
    \item \href{https://mlsys.org/Conferences/2026/CallForTravelGrants}{MLSys 2026 Student Travel Grant} \dateright{May 2026}
    \item \href{https://modal.com/academics}{Modal for Academics Grant} (USD 10,000) \dateright{Apr 2026}
    \item \href{https://thinkingmachines.ai/blog/tinker-research-and-teaching-grants/}{Tinker Research Grant} from Thinking Machines (USD 5,000) \dateright{Feb 2026}
    \item \href{https://grad.uw.edu/funding_posts/graduate-student-conference-presentation-awards/}{Graduate Student Conference Presentation Awards} from UW (USD 500) \dateright{Nov 2025}
    \item \href{https://www.cs.washington.edu/academics/graduate/phd-program/handbook/funding-fellowships/travel-grants/}{Allen School Travel Grant} from UW CSE (USD 500) \dateright{May 2024}
    \item{\bf Ph.D. Scholarship from \href{https://www.toyotariken.jp/en/}{Toyota Physical and Chemical Research Institute}}\\
    {\it Full tuition/insurance fee and stipend for two years (JPY 10,000,000/year)} \dateright{2023 -- 2025}\\
    {\it Additional financial aid of USD 6,000/year} \dateright{2025 -- Present}
    \item \href{https://iscaconf.org/isca2022/}{ISCA 2022} Registration Grant from \href{https://sites.google.com/wisc.edu/uarch2022/}{4th uArch workshop} \dateright{Jun 2022}
    \item \href{https://iscaconf.org/isca2021/}{ISCA 2021} Registration Grant from \href{https://sites.google.com/wisc.edu/uarch2021/}{3rd uArch workshop} \dateright{Jun 2021}
    \item Travel Grant to Chulalongkorn University by JASSO \dateright{Aug 2019}
    \item Gold Award, Chemistry Grand Prix
    \dateright{2018}
    \item Rank A Award, Japan Mathematical Olympiad
    \dateright{2018}
    \item Rank A Award, Japan Junior Mathematical Olympiad
    \dateright{2016}
\end{itemize}

% mentoring
\cvheading{Mentoring}

\begin{itemize}
    \item \href{https://zhudiangg.github.io/}{Xikai Meng} (UW ECE) \dateright{Spring 2026 -- Present}\\
    {\it M* and VibeServe}
    \item \href{https://www.linkedin.com/in/garv-ghai/}{Garv Ghai} (Georgia Tech) \dateright{Spring 2026 -- Present}\\
    {\it VoxServe and multimodal serving}
    \item \href{https://rubywtl.github.io/}{Wei-Tzu (Ruby) Lee} (UW ECE $\rightarrow$ Software Engineer at AWS) \dateright{Fall 2025 -- Present}\\
    {\it First author of Murmur (MLSys 2026 YPS)}
    \item \href{https://tang-t21.github.io/}{Tian Tang} (Tsinghua University $\rightarrow$ MTS at \href{https://nex-agi.com/}{Nex}) \dateright{Spring -- Summer 2024}\\
    {\it Co-first author of Fiddler (ICLR 2025)}
\end{itemize}

% Teaching
\cvheading{Teaching}

\begin{itemize}
    \item TA, \href{https://courses.cs.washington.edu/courses/cse554/26wi/}{CSE 554 Machine Learning Systems (Winter 2026)}
\end{itemize}

% Talks
\cvheading{Talks}

\begin{itemize}
% vibeserve
\item 
\talktitle{VibeServe: Can AI Agents Build Bespoke LLM Serving Systems?}
\talkloc{{NVIDIA TRT-LLM Team}, June 2026.} \\
\talkloc{\href{https://netlab.cs.washington.edu/}{UW Mobile Intelligence Lab.}, May 2026.}
\label{talk:vibeserve}

% FPGA seminar
\item 
\talktitle{Practical FPGA Development Seminar}
\talkloc{\href{https://www.fixstars.com/ja/news/2198/}{Fixstars FPGA Seminar vol. 10}, May 2022.} \\
\talkloc{\href{https://www.fixstars.com/ja/news/2192/}{Fixstars FPGA Seminar vol. 8}, March 2022.}

\item 
\talktitle{\href{https://ipsj.ixsq.nii.ac.jp/ej/index.php?active_action=repository_view_main_item_detail&page_id=13&block_id=8&item_id=217221&item_no=1}{Accelerating Decision Tree Ensemble with Guided Branch Approximation} (in Japanese).}
\talkloc{\href{https://www.ieice.org/ken/program/index.php?tgs_regid=5d4661bcd72ca9e43adb2d8bbf065908894cc838bab03bd6a85ecd2536a810e6&update=1}{ETNET 2022}, March 2022.}\label{talk:2022etnet}

\item 
\talktitle{\href{https://indico.cern.ch/event/950229/}{Pre-conditioners applied to ROOT compression algorithms}.}
\talkloc{IRIS-HEP/GSoC Student Presentations, September 2020.}
\label{talk:2020gsoc}

\end{itemize}

% Media
\cvheading{Media}

\begin{itemize}
\item 
\talktitle{\href{https://www.geekwire.com/2025/inside-the-uw-allen-school-six-grand-challenges-shaping-the-future-of-computer-science/}{Inside the UW Allen School: Six `grand challenges' shaping the future of computer science}.}
\talkloc{GeekWire, featuring VoxServe and ConsumerBench.}
\label{talk:2025geekwire-openhouse}

\end{itemize}

\cvheading{Services}
\needspace{3\baselineskip}\noindent Conference Reviewing
\begin{tasks}(4)
    \task NeurIPS (2026)
    \task \href{https://www.caisconf.org/program/2026/committee/}{CAIS (2026)}
    \task \href{https://icml.cc/Conferences/2026/ProgramCommittee}{ICML (2026)}
    \task \href{https://mlsys26.hotcrp.com/users/pc}{MLSys (2026)}
    \task \href{https://iclr.cc/Conferences/2026/ProgramCommittee}{ICLR (2026)}
\end{tasks}
\needspace{3\baselineskip}\noindent Journal Reviewing
\begin{itemize}
    \item TMLR (2025 -- Present)
\end{itemize}
\needspace{3\baselineskip}\noindent Workshop Reviewing
\begin{itemize}
    \item \href{https://wdlctc.github.io/efficient-reasoning-2026/}{COLM 2026 Workshop on Efficient Reasoning}
    \item \href{https://mmragi.github.io/mmragi/}{CVPR 2026 Multi-Modal Reasoning for AI Agents Workshop}
    \item \href{https://sites.google.com/view/memagent-iclr26/}{ICLR 2026 MemAgents Workshop}
    \item \href{https://sites.google.com/ucsd.edu/efficient-spatial-reasoning/}{ICLR 2026 ES-Reasoning Workshop}
    \item \href{https://efficient-reasoning.github.io/}{NeurIPS 2025 Workshop on Efficient Reasoning}
\end{itemize}
\needspace{3\baselineskip}\noindent Artifact Evaluation
\begin{tasks}(4)
    \task \href{https://sosp26ae.hotcrp.com/users/pc}{SOSP (2026)}
    \task \href{https://cais26-ae.hotcrp.com/users/pc}{CAIS (2026)}
    \task \href{https://sysartifacts.github.io/eurosys2026/organizers}{EuroSys (2026)}
    \task \href{https://www.microarch.org/micro58/submit/artifacts.php}{MICRO (2025)}
\end{tasks}
\needspace{3\baselineskip}\noindent Departmental Service
\begin{itemize}
    \item \href{https://www.cs.washington.edu/academics/graduate/phd-program/phd-admissions/pams/}{Allen School Pre-Application Mentorship Service (PAMS) Mentor} \dateright{2025}
    \item Allen School Ph.D. Admission Committee Member \dateright{2023 -- 2024}
    \item Allen School Ph.D. Admission Student Area Chair (Architecture) \dateright{2024}
\end{itemize}
\needspace{3\baselineskip}\noindent Miscellaneous
\begin{itemize}
    \item \href{https://gakuiryugaku.net/english}{The Japanese Graduate Student Association in the United States (JGSAU)} Committee Member \dateright{2023 -- 2026}
    \item \href{https://xplane.jp/tag/sop-writing-support/}{XPLANE SoP Writing Support Program} Mentor \dateright{2023 -- Present}
\end{itemize}

\cvheading{Skills}
\begin{itemize}
    \item {\bf Programming Languages}: C, C++, Python, CUDA, Triton, JavaScript, Verilog, SystemVerilog, Chisel, OCaml, Scala, R
    \item {\bf ML Systems \& Serving}: PyTorch, vLLM, SGLang, TensorRT-LLM, FlashInfer, Hugging Face, TVM, FAISS
    \item {\bf Hardware \& Simulation}: Vivado, Vitis, Pynq, ChampSim, gem5
\end{itemize}

\vspace{3mm}
\rightline{\color{black!60}\itshape Last update: July 11, 2026}
\end{document}